Beam-Helicity and Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS (v0.6)} \underline{Drafting Committee: DC90 (\today)}

### 2011-02-24 background_and_systematic.tex
Fixed some typos and rewrote some parts for clarification

\blue{The data sample in the exclusive region contains events involving both production of real photons in which the proton remains intact and events involving the excitation of the target proton to a $\Delta^+$ resonant state. As the recoiling proton is not detected the separation of the latter events is not possible.}
No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal. A Monte Carlo calculation based on the parameterisation of Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin. The results, denoted associated fraction and labelled ``\blue{A}ssoc. fraction'', are shown in the last row of each figure in the results section. The method used to perform the estimation is described in detail in
Ref.~\cite{Air08}.

>>>>

\blue{The data sample in the exclusive region contains events involving both production of real photons in which the proton remains intact and events involving the excitation of the target proton to a $\Delta^+$ resonant state. As the recoiling proton is not detected, separation of the latter events from the data sample is not possible.}
No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal. A Monte Carlo calculation based on the parameterisation of Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin. The results, denoted associated fraction and labelled ``\blue{A}ssoc. fraction'', are shown in the last row of each figure in the results section. The method used to perform the estimation is described in detail in
Ref.~\cite{Air08}.

### 2011-02-24 experiment_and_data.tex
Fixed some typos and rewrote some parts for clarification

The DVCS asymmetry amplitude $A^{\sin\phi}_{\textrm{LU,DVCS}}$ has a
contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ function,
which is bilinear in CFFs. \blue{However, this amplitude is inherently small at HERMES kinematic conditions due to the size of the $s_{1}^{\textrm{DVCS}}$ Fourier coefficient compared to the $s_{1}^{\textrm{I}}$ coefficient.} As a result of
the more complicated dependence on the CFFs and this suppression, it
will be more difficult to extract useful information for the constraint of GPDs
from the measurement of $A^{\sin\phi}_{\textrm{LU,DVCS}}$ than from the
kinematically-unsuppressed leading-twist amplitudes.

>>>>

The DVCS asymmetry amplitude $A^{\sin\phi}_{\textrm{LU,DVCS}}$ has a
contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ function,
which is bilinear in CFFs. \blue{However, this amplitude is inherently small at HERMES kinematic conditions due to the size of the $s_{1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{n}^{\textrm{BH}}$ coefficients in the denominator of Eq.~\ref{e:aludvcs}}. As a result of
the more complicated dependence on the CFFs and this suppression, it
will be more difficult to extract useful information for the constraint of GPDs
from the measurement of $A^{\sin\phi}_{\textrm{LU,DVCS}}$ than from the
kinematically-unsuppressed leading-twist amplitudes.

### 2011-02-24 results.tex
sentence removed
Fixed some typos and rewrote some parts for clarification

\begin{figure}
 \begin{center}
 \includegraphics[width=15cm]{bsadvcsplots_tc_xbjrange_eml_par13_bin6_9607_pic_update}
  \caption{\blue{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes}
from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges. The error bars (bands) represent the statistical
(systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the imprecision of
the beam polarisation measurement.}}
  \label{bsa_xbjrange}
 \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=15cm]{bcaplots_tc_xnjrange_eml_par13_bin6_9607_pic}
    \caption{\blue{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges. The error bars (bands) represent the statistical (systematic) uncertainties.  Theoretical calculations from the model described in \cite{Kum09} are shown as solid and dashed lines. See text for details. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}}
  \label{bca_xbjrange}
 \end{center}
\end{figure}

@@

The asymmetry amplitudes shown in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} were also re-binned as a function of $-t$ for three different ranges of $x_{\textrm{B}}$. There was no observed dependence of any of the amplitudes with this two dimensional binning.

>>>>

\begin{figure}
 \begin{center}
 \includegraphics[width=15cm]{bsadvcsplots_tc_xbjrange_eml_par13_bin6_9607_pic_update}
  \caption{\blue{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes}
from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges. The error bars (bands) represent the statistical
(systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the imprecision of
the beam polarisation measurement.}}
  \label{bsa_xbjrange2}
 \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=15cm]{bcaplots_tc_xnjrange_eml_par13_bin6_9607_pic}
    \caption{\blue{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges. The error bars (bands) represent the statistical (systematic) uncertainties.}}
  \label{bca_xbjrange2}
 \end{center}
\end{figure}

@@

\blue{In order to provide more detailed information for future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}. There is no observed $-t$ dependnece on any of the $A_{\textrm{LU}}$ amplitudes in either of the distinct ranges of $x_{\textrm{B}}$. Also no additional features or $-t$ dependencies are observed for the $A_{\textrm{C}}$ amplitudes in these separate $x_{\textrm{B}}$ ranges.}

### 2011-02-24 theory.tex
Fixed some typos and rewrote some parts for clarification

Generalised parton distributions depend upon four kinematic variables: the
Mandelstam variable $t=(p-p^{\prime})^2$, which is the squared momentum
transfer to the target nucleon in the scattering process with $p$ ($p^{\prime}$)
representing the initial (final) four momentum of the proton; the average
fraction $x$ of the nucleon's longitudinal momentum carried by the active
quark throughout the scattering process; half the difference in the
change of the fraction of the nucleon's longitudinal momentum carried by the
active quark at the start and end of the process, written as the skewness
variable $\xi$; and the square $-Q^2=q^2$ of the \blue{of the four-momentum of the virtual photon that mediates the lepton-proton scattering process.}. In the Bjorken limit of $Q^2\rightarrow\infty$ with
fixed $t$, $\xi$ is related to the Bjorken variable
$x_{\textrm{B}}=\frac{-q^2}{2p.q}$ as
$\xi\approx\frac{x_\textrm{B}}{2-x_\textrm{B}}$. The results are presented
against $x_{\textrm{B}}$ because there is no consensus on an experimentally
observable representation of $\xi$.

>>>>

Generalised parton distributions depend upon four kinematic variables: the
Mandelstam variable $t=(p-p^{\prime})^2$, which is the squared momentum
transfer to the target nucleon in the scattering process with $p$ ($p^{\prime}$)
representing the initial (final) four momentum of the proton; the average
fraction $x$ of the nucleon's longitudinal momentum carried by the active
quark throughout the scattering process; half the difference in the
change of the fraction of the nucleon's longitudinal momentum carried by the
active quark at the start and end of the process, written as the skewness
variable $\xi$; and the square $-Q^2=q^2$ of the \blue{of the four-momentum of the virtual photon that mediates the lepton-proton scattering process.} In the Bjorken limit of $Q^2\rightarrow\infty$ with
fixed $t$, $\xi$ is related to the Bjorken variable
$x_{\textrm{B}}=\frac{-q^2}{2p.q}$ as
$\xi\approx\frac{x_\textrm{B}}{2-x_\textrm{B}}$. The results are presented
against $x_{\textrm{B}}$ because there is no consensus on an experimentally
observable representation of $\xi$.
